---
title: My dynamic report
output: html_fragment
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
```



```{css} 

h2 {
    color: white; font-size: 40px; padding: 30px 0; background-color: #FF3399; width: 100%; margin-top: 150px; border-radius: 12px;
}
h3 {
    background-color: #FF1A66; color: white; padding: 20px; border-radius: 10px; margin: 10px auto; width: 50%;
}
body {
    margin: 0px; background-color: #FFD6E0; font-family: Arial, sans-serif; color: black; font-weight: bold; font-size: 18px; text-align: center;
}
p {
    background-color: #FF1A66; color: white;padding: 20px; border-radius: 10px; margin: 20px auto; width: 50%;
}
img {
    border: 4px solid white; padding: 6px; margin-bottom: 6px; background-color: #FF1A66;
}
```



## TikTok Engagement Analysis

### This report investigates TikTok observation data collected from user interaction tracking. It focuses and analysis  how different content types influence user engagement, including content observed, likes, comments, time spent on videos and other various social media interactions.

```{r R Code and Variables Setup}
library(tidyverse)
library(magick)

options(scipen = 999)

form_url <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vSPBYGP-4GkShen3QbePKIV-teDcVEAChx29SlLDv66E8pq2c9mZoyjnjLi-3wMG7haQK8py3fHbhHM/pub?gid=1545803211&single=true&output=csv"

logged_data <- read_csv(form_url)
latest_data <- logged_data %>%
  rename(Content_type = `What type of content was observed?`, 
         Likes = `How many likes did the content have?`, 
         Comments = `How many comments did the content have?`,
         Interaction = `How did you interact with the TikTok?`,
         Time_spent = `How much time was spent on the content? (Seconds)`,
         Finished = `Did you watch the video until the end?`)

media_vec <- c("Media / Entertainment (Film, TV, Animation, Art, Memes, Dance, etc)" = "Media / Entertainment")

latest_data$User_Engagement <- latest_data$Interaction != "Scrolled past (no interaction)"
```
 
 
 
### Meme: TikTok Scrolling Behaviour

```{r Meme: TikTok Scrolling Behaviour}
# Meme Creation

# ----- Image URL Links -----
reject_url <- "https://i.pinimg.com/736x/25/ac/84/25ac84d26005bfaaf611f29b96993c62.jpg"
accept_url <- "https://i.pinimg.com/736x/05/97/ab/0597abc9675b9f229e53e64ee82856ba.jpg"

# ----- Load and prepare images -----
reject_img <- image_read(reject_url) %>%
  image_scale("500x600!") %>%
  image_extent("500x600", gravity = "center")

accept_img <- image_read(accept_url) %>%
  image_scale("500x600!") %>%
  image_extent("500x600", gravity = "center")

# ----- Load and prepare text -----
width = 500
height = 600

reject_text <- image_blank(width, height, color = "white") %>%
  image_annotate(text = "Scrolling on \nTikTok", color = "black", size = 55, font = "Arial", gravity = "center")

accept_text <- image_blank(width, height, color = "white") %>%
  image_annotate(text = " Scrolling on Tiktok \n for Project 2", color = "black", size = 55, font = "Arial", gravity = "center")

# ----- Format Border -----
hori_line <- image_blank(width = 1030, height = 10, color = "black")
vert_line <- image_blank(width = 10, height = 600, color = "black")

reject_row <- image_append(c(vert_line, reject_text, vert_line, reject_img, vert_line))
accept_row <- image_append(c(vert_line, accept_text, vert_line, accept_img, vert_line))

project2_meme <- image_append(c(hori_line, reject_row, hori_line, accept_row, hori_line), stack=TRUE) %>%
  image_scale(700)

# ----- Write and Call -----
image_write(project2_meme, "project2_meme.png")
project2_meme
```



## Plot 1: Distribution of TikTok Content Types

This section examines the distribution of different types of TikTok content. The number of TikToks for Sports content is `r sum(latest_data$Content_type == "Sports", na.rm = TRUE)`, compared to the total of `r length(latest_data$Content_type)`.

```{r Plot 1: Distribution of TikTok Content Types}
ggplot(latest_data, aes(x = Content_type, fill = Content_type)) +
  geom_bar() +
  labs(title = "Number of TikToks \nby Content Type",
       x = "Content Type",
       y = "Number of TikToks") +
  guides(fill = "none") +
  theme_minimal() +
  coord_flip() +
  scale_x_discrete(labels = media_vec) +
  theme(plot.title = element_text(size = 16, face = "bold", margin = margin(b = 33), hjust = 0.5),
        axis.title.x = element_text(size = 12, face = "bold", margin = margin(t = 33)),
        axis.title.y = element_text(size = 12, face = "bold", margin = margin(r = 33)),
        axis.text.y = element_text(size = 10, face  = "bold", color="black"),
        axis.text.x = element_text(size = 10, face  = "bold", color="black"),
        axis.text.x.bottom = element_text(color = "black"))
```



## Plot 2: Time Spent by User Engagement

This section analyses how much time users spend on TikToks where engagement occurred. Engagement includes interaction such as liking, commenting, reposting, etc. The average time spent on content with user engagement is `r round(mean(latest_data$Time_spent[latest_data$User_Engagement == TRUE], na.rm = TRUE))`, as opposed to the average of all content (Interacted and Non Interacted), which is `r round(mean(latest_data$Time_spent, na.rm = TRUE))` second(s).

```{r Plot 2: Time Spent by User Engagement}
ggplot(latest_data, aes(x = User_Engagement, y = Time_spent, fill = User_Engagement)) +
  geom_bar(stat = "summary", fun = "mean") + 
  scale_fill_manual(values = c("FALSE" = "red", "TRUE" = "green")) +
  scale_x_discrete(labels = c("TRUE" = "Yes","FALSE" = "No")) +
  labs(title = "Time Spent by User Engagement",
       x = "Interaction",
       y = "Average Time (Seconds)") +
  guides(fill = "none") +
  theme_minimal() +
  theme(plot.title = element_text(size = 16, face = "bold", margin = margin(b = 33), hjust = 0.5),
        axis.title.x = element_text(size = 12, face = "bold", margin = margin(t = 33)),
        axis.title.y = element_text(size = 12, face = "bold", margin = margin(r = 33)),
        axis.text.y = element_text(size = 10, face  = "bold", color="black"),
        axis.text.x = element_text(size = 10, face  = "bold", color="black"),
        axis.text.x.bottom = element_text(color = "black"))
```



## Plot 3: Average Comments by Content Type

This section investigates the mean numbers comments on Tiktok by content type. Media / Entertainment content tends to recieve an average of `r round(mean(latest_data$Comments[latest_data$Content_type == "Media / Entertainment (Film, TV, Animation, Art, Memes, Dance, etc)"], na.rm = TRUE))` comments, in contrast to the `r round(mean(latest_data$Comments, na.rm = TRUE))` average of all content.

```{r Plot 3: Average Comments by Content Type}
ggplot(latest_data, aes(x = Content_type, y = Comments, fill = Content_type)) +
  geom_bar(stat = "summary", fun = "mean") +
  labs(title = "Average Number of \nComments by Content Type",
       x = "Content Type",
       y = "Average Number of Comments") +
  guides(fill = "none") +
  theme_minimal() +
  scale_x_discrete(labels = media_vec) +
  coord_flip() +
  theme(plot.title = element_text(size = 16, face = "bold", margin = margin(b = 33), hjust = 0.5),
        axis.title.x = element_text(size = 12, face = "bold", margin = margin(t = 33)),
        axis.title.y = element_text(size = 12, face = "bold", margin = margin(r = 33)),
        axis.text.y = element_text(size = 10, face  = "bold", color="black"),
        axis.text.x = element_text(size = 10, face  = "bold", color="black"),
        axis.text.x.bottom = element_text(color = "black"))
```
