---
title: My dynamic report
output: html_fragment
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```


```{css}
h1 {
    color: red; font-family: Arial; font-weight: bold; font-size: 100px; padding: 40px; background-color: white; text-align: center; display: inline-block;     margin: 50px auto 0;
}
h2 {
    color: white; font-family: Arial; font-size: 40px; font-weight: bold; padding: 30px 0; background-color: #FF3399; text-align: center; width: 100%;          margin-top: 150px; display: block; border-radius: 12px;
}
h3 {
    background-color: #FF1A66; color: white; font-weight: bold; text-align: center; padding: 20px; border-radius: 10px; margin: 20px auto; width: 50%;
}
body {
    margin: 0px; background-color: #FFD6E0; font-family: Arial, sans-serif; color: black; font-weight: bold; font-size: 18px; text-align: center;
}
p {
    background-color: #FF1A66; color: white; font-weight: bold; text-align: center; padding: 20px; border-radius: 10px; margin: 20px auto; width: 50%;
}
img {
    border: 4px solid #FF3399; padding: 6px; margin-bottom: 6px; background-color: #FF1A66;
}
a {
    color: white; text-decoration: underline;
}
```

# TikTok Engagement Analysis

### This report investigates TikTok observation data collected from user interaction tracking. It focuses and analysis  how different content types influence user engagement, including content observed, likes, comments, time spent on videos and other various social media interactions.

```{r}
# Data and Code Setup
library(tidyverse)

options(scipen = 999)

form_url <- "https://docs.google.com/spreadsheets/d/e/2PACX-1vSPBYGP-4GkShen3QbePKIV-teDcVEAChx29SlLDv66E8pq2c9mZoyjnjLi-3wMG7haQK8py3fHbhHM/pub?gid=1545803211&single=true&output=csv"

logged_data <- read_csv(form_url)
latest_data <- logged_data %>%
  rename(Content_type = `What type of content was observed?`, 
         Likes = `How many likes did the content have? (Enter full number)`, 
         Comments = `How many comments did the content have? (Enter full number)`,
         Interaction = `How did you interact with the TikTok?`,
         Time_spent = `Time (Seconds) spent on the content?`,
         Finished = `Did you watch the video until the end?`)


media_vec <- c("Media / Entertainment (Film, TV, Animation, Art, Memes, Dance, etc)" = "Media / Ent")

latest_data$User_Engagement <- latest_data$Interaction != "Scrolled past (no interaction)"
```


## Plot 1

This section examines the distribution of different types of TikTok content. The number of Tiktoks for Sports content is `r sum(latest_data$Content_type == "Sports", na.rm = TRUE)`, compared to the total of `r length(latest_data$Content_type)`.

```{r}
ggplot(latest_data, aes(x = Content_type, fill = Content_type)) +
  geom_bar() +
  labs(title = "Number of Tiktoks by Content Type",
       x = "Content Type",
       y = "Count") +
  guides(fill = "none") +
  theme_minimal() +
  coord_flip() +
  scale_x_discrete(labels = media_vec) +
  theme(plot.title = element_text(size = 16, face = "bold", margin = margin(b = 33)),
        axis.title.x = element_text(size = 12, face = "bold", margin = margin(t = 33)),
        axis.title.y = element_text(size = 12, face = "bold", margin = margin(r = 33)),
        axis.text.y = element_text(size = 10, face  = "bold", color="black"),
        axis.text.x = element_text(size = 10, face  = "bold", color="black"),
        axis.text.x.bottom = element_text(color = "black"))
```



## Plot 2

This section analyses how much time users spend on Tiktoks where engagement occurred. Engagement includes interaction such as liking, commenting, reposting, etc. The average time spent on content with user engagement is `r round(mean(latest_data$Time_spent[latest_data$User_Engagement == TRUE], na.rm = TRUE))`, as opposed to the average of all content (Interacted and Non Interacted), which is `r round(mean(latest_data$Time_spent, na.rm = TRUE))` second(s).

```{r}
ggplot(latest_data, aes(x = User_Engagement, y = Time_spent, fill = User_Engagement)) +
  geom_bar(stat = "summary", fun = "mean") + 
  scale_fill_manual(values = c("FALSE" = "red", "TRUE" = "green")) +
  scale_x_discrete(labels = c("TRUE" = "Yes","FALSE" = "No")) +
  labs(title = "Time Spent by User Engagement",
       x = "Interaction",
       y = "Average Time (Seconds)") +
  guides(fill = "none") +
  theme_minimal() +
  theme(plot.title = element_text(size = 16, face = "bold", margin = margin(b = 33)),
        axis.title.x = element_text(size = 12, face = "bold", margin = margin(t = 33)),
        axis.title.y = element_text(size = 12, face = "bold", margin = margin(r = 33)),
        axis.text.y = element_text(size = 10, face  = "bold", color="black"),
        axis.text.x = element_text(size = 10, face  = "bold", color="black"),
        axis.text.x.bottom = element_text(color = "black"))
```



## Plot 3

This section investigates the mean numbers comments on Tiktok by content type. Media/Ent content tends to recieve an average of `r round(mean(latest_data$Comments[latest_data$Content_type == "Media / Entertainment (Film, TV, Animation, Art, Memes, Dance, etc)"], na.rm = TRUE))` comments, in contrast to the `r round(mean(latest_data$Comments, na.rm = TRUE))` average of all content.

```{r}
ggplot(latest_data, aes(x = Content_type, y = Comments, fill = Content_type)) +
  geom_bar(stat = "summary", fun = "mean") +
  labs(title = "Average number of Comments by Content Type",
       x = "Content Type",
       y = "Average Comments") +
  guides(fill = "none") +
  theme_minimal() +
  scale_x_discrete(labels = media_vec) +
  coord_flip() +
  theme(plot.title = element_text(size = 16, face = "bold", margin = margin(b = 33)),
        axis.title.x = element_text(size = 12, face = "bold", margin = margin(t = 33)),
        axis.title.y = element_text(size = 12, face = "bold", margin = margin(r = 33)),
        axis.text.y = element_text(size = 10, face  = "bold", color="black"),
        axis.text.x = element_text(size = 10, face  = "bold", color="black"),
        axis.text.x.bottom = element_text(color = "black"))
```
